# Calculating total genome numbers for each profiler
## Set up
```{r}
suppressPackageStartupMessages(
  {
  library(taxonomizr)
  library(tidyverse)
  library(stringr)
  library(rentrez)
  library(geneviewer)
  }
)

```

## Metascope/Pathoscope
### Method 1 (use accession numbers)
#### Read files
```{r}
## zgrep '^>' bacteria.fasta.gz >> "metascope_bacteria_raw.txt"

bacteria <- "metascope/metascope_bacteria_raw.txt"
fungi <- "metascope/metascope_fungi_raw.txt"
viral <- "metascope/metascope_viral_raw.txt"

line_bacteria <- readLines(bacteria)
line_fungi <- readLines(fungi)
line_viral <- readLines(viral)

all_lines <- c(line_bacteria, line_fungi, line_viral)

```
#### Convert to taxid using taxonomizr
```{r}
accession_numbers <- as.vector(str_extract(all_lines, "(?<=^>)[^ ]+"))

taxid <- taxonomizr::accessionToTaxa(accession_numbers, sqlFile = "../../../../taxonomizr_db/accessionTaxa.sql")
```

```{r}
length(taxid)
```
#### Process NA from taxonomizr using rentrez (NCBI eutils)
```{r}
sum(is.na(taxid))
```

```{r}
line_retry_taxid <- readLines("metascope/batch_process_na/results/metascope_na_NCBI.txt")
```
#### Total genomes for metascope
```{r}
total_taxid_metascope <- c(taxid, line_retry_taxid)
unique_taxid_metascope <- unique(total_genomes_metascope)
total_genome_metascope_pathoscope2 <- length(unique_taxid_metascope)
total_genome_metascope_pathoscope2
```

<!-- ### Method 2 (column extraction) -->

<!-- ```{r} -->
<!-- split_words <- strsplit(all_lines, " ") -->
<!-- names <- sapply(split_words, function(x) paste(x[2], x[3])) -->
<!-- unique_names <- unique(names) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- length(unique_names) -->
<!-- ``` -->

## Kraken2/Bracken
### Calculate total genomes directly from the map file
```{r}
kraken <- "../../../../../aubrey/newMB_02_25_meta_benchmark/db/StandardKrakenDB/seqid2taxid.map"
read_kraken <- readLines(kraken)
split_kraken <- str_extract(read_kraken, "(?<=\t)\\d+")
unique_taxid <- unique(split_kraken)
total_genome_kraken_bracken <- length(unique_taxid)
total_genome_kraken_bracken
```

## Centrifuge
### Read files from conversion table
### Remove synthetic constructs (taxid 32630)
```{r}
centrifuge <- "centrifuge/centrifuge_conversion.txt"
read_centrifuge <- readLines(centrifuge)
split_centrifuge <- str_extract(read_centrifuge, "(?<=\t)\\d+")
unique_taxid_without_32630 <- unique(split_centrifuge[split_centrifuge != "32630"])
total_genome_centrifuge <- length(unique_taxid_without_32630)
total_genome_centrifuge

```






<!-- ### accession numbers -->
<!-- ```{r} -->
<!-- centrifuge <- "centrifuge/centrifuge_con.txt" -->
<!-- all_lines_centrifuge <- readLines(centrifuge) -->
<!-- line_with_accessions_centrifuge <- all_lines_centrifuge[1:8243] -->
<!-- split_centrifuge_accessions <- strsplit(line_with_accessions_centrifuge, split = " ") -->
<!-- centrifuge_accessions <- sapply(split_centrifuge_accessions, function(x) x[[1]]) -->
<!-- ``` -->
<!-- #### 1 -->
<!-- ```{r} -->
<!-- accessions_taxid_centrifuge_taxonomizr <- taxonomizr::accessionToTaxa(centrifuge_accessions, sqlFile = "../../../../taxonomizr_db/accessionTaxa.sql") -->
<!-- length(unique(accessions_taxid_centrifuge_taxonomizr)) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- sum(is.na(accessions_taxid_centrifuge)) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- na_position_accession <- which(is.na(accessions_taxid_centrifuge)) -->
<!-- na_accession_centrifuge <- centrifuge_accession[na_position_accession] -->
<!-- ``` -->
<!-- ### use batch entrez NCBI for centrifuge accession -->
<!-- ```{r} -->
<!-- write.table(na_accession_centrifuge, file = "centrifuge/centrifuge_na_accession.txt", row.names = FALSE, col.names = FALSE, quote = FALSE) -->
<!-- ``` -->

<!-- #### 2 -->
<!-- ```{r} -->
<!-- lines_na_accession_centrifuge_ncbi <- readLines("centrifuge/results/centrifuge_success.txt") -->
<!-- ``` -->

<!-- ```{r} -->
<!-- accession_taxid_centrifuge <- c(lines_na_accession_centrifuge_ncbi, accessions_taxid_centrifuge_taxonomizr) -->
<!-- unique_accession_taxid_centrifuge <- unique(accession_taxid_centrifuge) -->
<!-- length(unique_accession_taxid_centrifuge) -->
<!-- ``` -->
<!-- ## accession lines + cid lines -->
<!-- # actual 1 -->
<!-- ```{r} -->
<!-- line_accession_cid <- readLines("centrifuge/centrifuge_conversion.txt") -->
<!-- line_accession_cid <- line_accession_cid[1:10692] -->
<!-- split_accession_cid_taxid <- str_extract(line_accession_cid, "(?<=\t)\\d+") -->

<!-- ``` -->


<!-- ## Clone vector lines -->
<!-- ```{r} -->
<!-- line_cv_centrifuge <- line_centrifuge[10693:14718] -->
<!-- write.table(line_cv_centrifuge, file = "centrifuge/centrifuge_cv.txt", row.names = FALSE, col.names = FALSE, quote = FALSE) -->
<!-- ``` -->
<!-- ### NCBI for cv -->
<!-- ```{r} -->

<!-- ``` -->

<!-- ## UniVec lines -->
<!-- ```{r} -->
<!-- line_UniVec_accession_centrifuge <- line_centrifuge[14719:length(line_centrifuge)] -->
<!-- split_centrifuge_UniVec <- as.vector(str_extract(line_UniVec_accession_centrifuge, "(?<=\\|)[^|:]+(?=:)")) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- length(split_centrifuge_UniVec) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- taxid_centrifuge_UniVec <- taxonomizr::accessionToTaxa(split_centrifuge_UniVec, sqlFile = "../../../../taxonomizr_db/accessionTaxa.sql") -->
<!-- ``` -->

<!-- ```{r} -->
<!-- sum(is.na(taxid_centrifuge_UniVec)) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- na_position_UniVec <- which(is.na(taxid_centrifuge_UniVec)) -->
<!-- na_UniVec_accession_centrifuge <- split_centrifuge_gnl[na_position_UniVec] -->
<!-- ``` -->


<!-- ### Use NCBI for uv accession centrifuge -->
<!-- ```{r} -->
<!-- write.table(na_UniVec_accession_centrifuge, file = "centrifuge/centrifuge_na_UniVec.txt", row.names = FALSE, col.names = FALSE, quote = FALSE) -->
<!-- ``` -->

<!-- #### 3 -->
<!-- ```{r} -->
<!-- taxid_centrifuge_na_uv <- readLines("centrifuge/results/centrifuge_combined_uv_success.txt") -->

<!-- ``` -->

